A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-06-01 bioc-workflow.Rmd
add short paragraph about pdata

The feature meta-data is stored in the `fData`
slot and can be accessed by `fData(lopit2016)`. When using
`readMSnSet2`, automatically, everything that is not defined as
quantitation data by `ecol` or the feature names by `fnames` is
deposited to the `fData` slot. As we wish to demonstrate the complete
analysis of this data we remove the results from the prior analysis
described in [@hyper] in the code chunk below. We see the `fData`
contains 25 columns describing information such as the number of
peptides, associated markers, machine learning results etc. For
demonstration in the code chunk below keep the 2nd, 8th and 11th
columns which contain the Uniprot entry names and two different marker
sets to use an input for machine learning analyses (see sections on
markers and subsequent sections).

```{r removefData}
fvarLabels(lopit2016)
fData(lopit2016) <- fData(lopit2016)[, c(2, 8, 11)]
head(fData(lopit2016))
```

@@

## Change featureNames of the MSnSet to match the marker names 
## which are named by Uniprot Entry Name
featureNames(lopit2016) <- make.unique(fData(lopit2016)[, 1])

>>>>

The feature meta-data is stored in the `fData`
slot and can be accessed by `fData(lopit2016)`. When using
`readMSnSet2`, automatically, everything that is not defined as
quantitation data by `ecol` or the feature names by `fnames` is
deposited to the `fData` slot. As we wish to demonstrate the complete
analysis of this data we remove the results from the prior analysis
described in [@hyper] in the code chunk below. We see the `fData`
contains 25 columns describing information such as the number of
peptides, associated markers, machine learning results etc.

For demonstration in the code chunk below keep the 2nd, 8th and 11th
columns which contain the Uniprot entry names and two different marker
sets to use an input for machine learning analyses (see sections on
markers and subsequent sections) and rename the first feature variable
names.

```{r removefData}
fvarLabels(lopit2016)
fData(lopit2016) <- fData(lopit2016)[, c(2, 8, 11)]
fvarLabels(lopit2016)[1] <- "UniProtId"
head(fData(lopit2016))
```

Note that when using the simple `readMSnSet2` procedure, sample
meta-data is kept empty. It is advised to annotate the fractions as
well. Below, we annotate the replicate from which the profiles
originate and the TMT tag (extracted from the sample/fraction names).

```{r pdata}
pData(lopit2016)$replicate <- rep(1:2, each = 10)
pData(lopit2016)$tag <- sub("\\.1$", "", sub("^X", "", sampleNames(lopit2016)))
pData(lopit2016)
```

@@

## Change featureNames of the MSnSet to match the marker names 
## which are named by Uniprot Entry Name
featureNames(lopit2016) <- make.unique(as.character(fData(lopit2016)[, 1]))
